Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-09 WRITEUP/ms.tex
Updates from Overleaf

Summarizing, the virial parameter can be used to quantify the stability/boundedness of 
%mm an MCC. 
    a molecular cloud.
Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
%
Such a criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.\DL{perhaps to be removed...}} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal
velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
%mm
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold  ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
clouds identified at low density cut (see top left panel of \Fig{dist})  
correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
%mm
      over all times analyzed here.
Note that the scalesshown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$. 
\label{fig:dist}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss27.pdf}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ ---accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).   \MM{I
  am inclined to leave the pressure confinement curves off of the
  final plot.}
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. Left panels show MCCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs identified using a high $n_{\rm cut}$\eq19\,\cc.
\label{fig:alpha16-28}}
\end{figure*}

\subsection{Single Evolutionary Stage}  \label{sec:singless}
\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), and identify a set of MCCs in each of them. Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right), respectively. Let us start from analyzing the accreting phase.

MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$ pc). These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs. here and in caption; in addition it would good to give the properties of this galaxy}. 
Sizes are somewhat dependent on the choice of $n_{\rm cut}$. As such density threshold is increased, some of the MCCs within the main disk break into multiple sub-MCCs. In this case, we effectively identify a population of denser molecular structures (see \Fig{MCC}). On the other hand, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.

@@

% Starburst 
Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ compared to the accreting phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
% PVE
We also compare the MCCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}). Dashed lines in the figure show the loci along which the given external pressures are needed for MCCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).
The MCCs in the satellite galaxies are found to follow the locus of
$\log{(P/\textrm{K cm}^{-3})}$\eq6, \MM{This is not shown in the
  figure.  If you want to claim it, it needs to be shown somewhere.} which
is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.

@@

The high pressure observed in \flower \MM{Where are pressures shown?
  You can't just draw them from the virial vs.\ surface density plot
  because that assumes equilibrium gas clouds, which these are clearly
  not, given their huge stellar contents.} is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, 
%mm they are likely form 
  MCCs are likely formed
by shock compression and cloud-cloud collisions 
%mm after large amounts of gas from the pair of progenitor galaxies
%are funneled toward the central region 
    that funnel large amounts of gas from the progenitor galaxies
    towards the central region
\citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may \MM{Do we have any
  evidence for or against this speculation?} also be the 
dominant mode for forming the highly supersonic massive MCCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
\citealt{Swinbank11a}) --- but the observed size scales could also
result from the resolution limit, while the true physical scales of
MCCs in $z$\,\ssim2 galaxies could be smaller.
%mm in reality.
%
The constant inter-cloud collisions as gas is being accreted onto the
main galaxy \MM{This is a highly dissipative process.  Hennebelle \&
  Klessen found it could only be important in rather small galaxies.
  Does \flower qualify?} would also render
the MCCs 
%mm to be 
gravitationally unbound (see e.g., \citealt{Dobbs11a}), \MM{Dobbs
  started with a low-density disk, and got low-density clouds. I don't
  think that's what you have here.  Do you have any evidence for
  inter-cloud collisions being important?} which is
consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.

% mass-size relation
The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
can be understood by acknowledging the fact that a H$_2$ molecular
cloud does not necessary contain CO (e.g., as CO forms deeper in
molecular clouds), and that our simulation does not have enough
resolution to directly form CO\footnote{In fact, to form CO and make
  predictions for CO line emission in the work presented by
  \citet{Vallini18a}, we model the internal structure of MCC within
  each cell in our simulation.}.  
\MM{But column densities have nothing to do with CO, and you are
  deriving $A_V$ from column densities.  Forming CO doesn't increase
  column densities; it is just a tracer of dense gas.  Atomic line
  cooling will be just as efficient as CO in actually cooling the gas
  down to tens of Kelvin (see Clark \& Glover some years ago).}
%
That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag 
%mm likely manifests from the fact 
    demonstrates
that the MCCs in our simulation have lower column densities than the
star-forming cores observed in the Milky Way, which are
observationally well-resolved within an MCC, and indeed, have
sufficient column density to form CO.  \MM{I suppose the question is
  if we observed the Milky Way at equivalent resolution, would we see
  such low column densities on average?  This is more or less the game
that Diderijk Kruijssen has been playing.}

@@

% different evolutionary stages
In the scaling relations examined, we find similar MCC properties in
relation to those observed in the nearby Universe between the
accreting phase and the starburst phase of \flower (see
\Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is
  trying to say.  These MCCs don't look similar to nearby objects to
  me... but then you make a comparison between phases?} That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr. \DL{some MCCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?} \MM{I'd say there is great
significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
stars, exactly what would be expected during a starburst.}

@@

% alpha parameters
As shown in \Fig{larsons_single},
the virial parameter of the sub-MCCs \MM{How can we distinguish
  sub-MCCs from MCCs in this figure?} is $\alpha_{\rm vir}\gtrsim10$,
which is considerably lower than their ``parent'' MCCs found in the
main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).  \MM{However,
  both are extremely high.}
%
For the MCCs in the satellite galaxies, \MM{How can we distinguish
  these, in turn?} a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the
weaker stellar feedback in the satellites \MM{Or lower stellar content
and thus weaker potentials?} as they have experienced fewer episodes
of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of
$\sim$0.1) \MM{This is what I would expect for molecular gas.  Should
  you explicitly show stellar-to-gas mass ratios in a figure?}.

% pext
As shown in \Fig{larsons_single},
MCCs in the main disk of \flower have higher pressure than the
sub-MCCs. \MM{Pressures are not shown in this figure, as noted
  above. If you want to demonstrate pressure, you need to actually
  examine the gas pressure field.} The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
%the MCC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales.
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCCs to be bound and collapse.

@@

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
thickness of its disk (via $\sigma_z$), some of these MCCs are
consistent with  $Q_{\rm eff} > 1$. 
\MM{Is your $Q_{\rm eff}$ based on your equation 11?  If not, you
  should probably show it's value explicitly, or else remove that
  section of the explanation [you don't want to leave the ``rifle on
  the wall''.]}. \DL{ this is based on Eqn 12.}
This demonstrates the importance of accounting for stellar contribution and disk thickness 
when examining the stability of molecular gas structures.
This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
that are preferentially being imaged at high resolution with ALMA.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).

>>>>

Summarizing, the virial parameter can be used to quantify the stability/boundedness of 
%mm an MCC. 
    a molecular cloud.
Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
%
Such a criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.

In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm cl} + M_{\star} }\,.
\label{eqn:alpha_tot}
\end{equation}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal
velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
%mm
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}. 
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. 
%
The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
clouds identified at low density cut (see top left panel of \Fig{dist})  
correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges ($M_{\star}/M_{\rm cl}$) between $<$\,0.1 to 70 over all the
MCCs identified across all evolutionary stages of \flower.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
 over all times analyzed here.
Note that the scalesshown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$. 
\label{fig:dist}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Blue circular symbols shown in the $\alpha_{\rm vir}$-mass plot shows the total virial parameters, including
the stellar contribution (see Equation~\ref{eqn:alpha_tot}).
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a, 
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are 
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).   
The gray dotted lines shown in the bottom panels correspond to the various external pressures for 
gas in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar). Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs 
identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
\label{fig:alpha16-28}}
\end{figure*}

\subsection{Single Evolutionary Stage}  \label{sec:singless}
\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), 
and identify a set of MCCs in each of them. \DL{note that delay in cloud properties and SFR.}
Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
such as the nearby gas-rich galaxy M64 and 
% Kennicutt, 1996IAUS..171...11K
% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
% with the inner gas disk the remnant of the
% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
the z\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
\citep{Rosolowsky05a, Swinbank11a}.
Since the sizes are somewhat dependent on the choice of $n_{\rm cut}$, as such, 
some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.

@@

% Starburst 
In the starburst phase, some MCCs have lower velocity dispersion, virial parameter, 
and $\sigma^2/R$ compared to the accreting phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
% PVE
We also compare the MCCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}). Dashed lines in the figure show the loci along which the given external pressures are needed for MCCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).
The MCCs in the satellite galaxies are found to follow the locus of
$\log{(P/\textrm{K cm}^{-3})}$\eq6, \MM{This is not shown in the
  figure.  If you want to claim it, it needs to be shown somewhere.} which
is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.

@@

The high pressure observed in \flower \MM{Where are pressures shown?
  You can't just draw them from the virial vs.\ surface density plot
  because that assumes equilibrium gas clouds, which these are clearly
  not, given their huge stellar contents.} is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, 
%mm they are likely form 
  MCCs are likely formed
by shock compression and cloud-cloud collisions 
%mm after large amounts of gas from the pair of progenitor galaxies
%are funneled toward the central region 
    that funnel large amounts of gas from the progenitor galaxies
    towards the central region
\citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may \MM{Do we have any
  evidence for or against this speculation?} also be the 
dominant mode for forming the highly supersonic massive MCCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
\citealt{Swinbank11a}) --- but the observed size scales could also
result from the resolution limit, while the true physical scales of
MCCs in $z$\,\ssim2 galaxies could be smaller.
%mm in reality.
%
The constant inter-cloud collisions as gas is being accreted onto the
main galaxy \MM{This is a highly dissipative process.  Hennebelle \&
  Klessen found it could only be important in rather small galaxies.
  Does \flower qualify?} would also render
the MCCs 
%mm to be 
gravitationally unbound (see e.g., \citealt{Dobbs11a}), \MM{Dobbs
  started with a low-density disk, and got low-density clouds. I don't
  think that's what you have here.  Do you have any evidence for
  inter-cloud collisions being important?}
\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
which is consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.

% mass-size relation
The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
can be understood by acknowledging the fact that a H$_2$ molecular
cloud does not necessary contain CO (e.g., as CO forms deeper in
molecular clouds), and that our simulation does not have enough
resolution to directly form CO\footnote{In fact, to form CO and make
  predictions for CO line emission in the work presented by
  \citet{Vallini18a}, we model the internal structure of MCC within
  each cell in our simulation.}.  
\MM{But column densities have nothing to do with CO, and you are
  deriving $A_V$ from column densities.  Forming CO doesn't increase
  column densities; it is just a tracer of dense gas.  Atomic line
  cooling will be just as efficient as CO in actually cooling the gas
  down to tens of Kelvin (see Clark \& Glover some years ago).}
\DL{It doesn't increase the column density, but these obs. results are based on CO, which traces deeper 
regions than we could here because MCCs are not entirely molecular, this may become clearer after 
expanding what $n_{\rm cut}$ means in Sec 3. {\bf AP?}}
%
That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag 
%mm likely manifests from the fact 
    demonstrates
that the MCCs in our simulation have lower column densities than the
star-forming cores observed in the Milky Way, which are
observationally well-resolved within an MCC, and indeed, have
sufficient column density to form CO.  \MM{I suppose the question is
  if we observed the Milky Way at equivalent resolution, would we see
  such low column densities on average?  This is more or less the game
that Diderijk Kruijssen has been playing.}
\DL{Don't think this is a resolution effect, but our MCC is not entirely H2 {\bf AP?}}

@@

% different evolutionary stages
In the scaling relations examined, we do not find any quantitative major differences
in the MCC properties with respect to those observed in the nearby Universe 
between the accreting phase and the starburst phase of \flower (see
\Fig{larsons_single}), which are separated by $\simeq$300\,Myr. 
However, between the two phases, {\bf blah...}
\DL{some MCCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?} \MM{I'd say there is great
significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
stars, exactly what would be expected during a starburst.}

@@

% alpha parameters
As shown in \Fig{larsons_single},
the virial parameter of the sub-MCCs \MM{How can we distinguish
  sub-MCCs from MCCs in this figure?} is $\alpha_{\rm vir}\gtrsim10$,
which is considerably lower than their ``parent'' MCCs found in the
main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).  \MM{However,
  both are extremely high.}
%
For the MCCs in the satellite galaxies, \MM{How can we distinguish
  these, in turn?} a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the
weaker stellar feedback in the satellites \MM{Or lower stellar content
and thus weaker potentials?} as they have experienced fewer episodes
of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of
$\sim$0.1) \MM{Should you explicitly show stellar-to-gas mass ratios in a figure?}.

% Pressure
MCCs in the main disk of \flower have higher pressure than the
sub-MCCs. \MM{examine the gas pressure field.} The lower virial parameter and 
pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
%the MCC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales.
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCCs to be bound and collapse.

@@

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are
consistent with  $Q_{\rm eff} > 1$. 
This demonstrates the importance of accounting for stellar contribution and disk thickness 
when examining the stability of molecular gas structures.
This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
that are preferentially being imaged at high resolution with ALMA.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).
